Adapting Duplicate Filters to a Sliding Window Context

### 2020-03-04 qhtv2.tex
fix proba optimal filter

	More precisely, it is possible to create a filter with a FNR of $0$, and a FPR of $\frac{1}{w}$.
\end{theorem}

\begin{proof}
	Let $h$ be a hash function with codomain $\{0,1\}^{2 \log_2 w}$.
The birthday theorem, as summed up in \cite{10.1007/3-540-45708-9_19}, states that for a hash function $h$ over $a$ bits, one must on average collect $2^{a/2}$ input-output pairs before obtaining a collision. Therefore $2^{2 \log_2 w / 2} = w$ values $h(e_i)$ can be computed before having a $50\%$ probability of a collision (here, a collision is when two distinct elements of the stream $e_i, e_j$ with $i \neq j, e_i \neq e_j$ have the same hash, i.e. $h(e_i) = h(e_j)$).

@@

There is no false negative, and a false positive only happens if the new element to be inserted collides with another element, which happens with probability $\frac 12\frac{2}{w}$, hence an FNR of $0$ and a FPR of $\frac{1}{w}$.
The queue stores $w$ hashes, and as such requires $w \cdot 2\log_2 w$ bits of memory.
\end{proof}

@@

Another remark is that when $M \approx w\log_2w$, it may be possible to solve the problem almost optimally in terms of error rate, the proposed solution remains very slow, requiring $O(W)$ computation time (although this complexity can be parallelized). Hence, it remains an open question of how to quickly detect duplicates in this context.

>>>>

	More precisely, it is possible to create a filter with a FNR of $0$, and a FPR of $1 - (1-\frac1{w^2})^w \sim \frac 1w$.
\end{theorem}

\begin{proof}
	Let $h$ be a hash function with codomain $\{0,1\}^{2 \log_2 w}$.
The birthday theorem, as summed up in \cite{10.1007/3-540-45708-9_19}, states that for a hash function $h$ over $a$ bits, one must on average collect $2^{a/2}$ input-output pairs before obtaining a collision. Therefore $2^{(2 \log_2 w) / 2} = w$ hash values $h(e_i)$ can be computed before having a $50\%$ probability of a collision (here, a collision is when two distinct elements of the stream $e_i, e_j$ with $i \neq j, e_i \neq e_j$ have the same hash, i.e. $h(e_i) = h(e_j)$).

@@

There is no false negative, and a false positive only happens if the new element to be inserted collides with at least one other element, which happens with probability $1 - (1 - \frac 1{2^{2\log_2w}})^{w} = 1 - (1-\frac1{w^2})^w$, hence an FNR of $0$ and a FPR of $1 - (1-\frac1{w^2})^w$.
The queue stores $w$ hashes, and as such requires $w \cdot 2\log_2 w$ bits of memory.
\end{proof}

@@

Another remark is that when $M \approx w\log_2w$, it may be possible to solve the problem almost optimally in terms of error rate, the proposed solution remains very slow, requiring $O(w)$ computation time (although this complexity can be parallelized). Hence, it remains an open question of how to quickly detect duplicates in this context.
